The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
remove some finished conversations

As an alternative morphological indicator (instead of \sersic index)
we use a bulge-to-total ratio derived from the double \sersic
profile fits.  This ratio is defined in terms of bulge and disk fluxes as
\begin{equation}
\frac{B}{T} = \frac{f_\text{bulge}}{f_\text{bulge}+f_\text{disk}}.
\end{equation}
(\rachel{Note, the equation that was previously in here was wrong.
  It's not defined in terms of surface brightnesses, but rather in
  terms of flux.  Were you using numbers from my files for $B/T$?  If
  so, then it was calculated properly.  But if your analysis uses the
  equation that was in here before, then you will have to redo it.
  Sorry for not noticing this earlier.}
 \arun{I didn't have to compute the ratios. Claire had it computed already. So nothing but the equation had to be changed.})

\rachel{I think it would be useful to take the entire sample that we
  use for science, and show the overall distributions of axis ratio,
  distortion (one curve for Claire's and one curve for
  re-Gaussianization), \sersic index, and \btt.  This would be a
  nearly full-page four panel figure, but I think it's worthwhile to
  illustrate the nature of the sample.  For example, it will clearly
  show why we cannot use the distributions of \sersic index and \btt,
  because of the hard cutoffs.} \arun{Done.}

>>>>

As an alternative morphological indicator (instead of \sersic index)
we use a bulge-to-total ratio derived from the double \sersic
profile fits.  This ratio is defined in terms of bulge and disk fluxes as
\begin{equation}
\frac{B}{T} = \frac{f_\text{bulge}}{f_\text{bulge}+f_\text{disk}}.
\end{equation}
